### 2008-08-05 doc/backend_interface/Backends.tex
backends doc update

\vspace*{3mm}
The following properties referring to job counts are obtained from GridManager's status files:

\begin{tabular}{|l|p{12cm}|}
\hline
Property & Meaning \\
\hline \hline
TotalJobs & Number of grid jobs which are not yet finished \\
\hline
RunningJobs & Number of grid jobs running \\
\hline
WaitingJobs & Number of grid jobs queued in the LRMS and waiting to be submitted to the LRMS \\
\hline
\end{tabular}

@@

\begin{tabular}{|l|p{12cm}|}
\hline
Property & Value\\
\hline \hline
URL & \texttt{https://\emph{hostname}:\emph{port}/arex} \\
\hline
Technology & \texttt{webservice} \\
\hline
Interface & \texttt{OGSA-BES} \\
\hline
WSDL & \texttt{https://\emph{hostname}:\emph{port}/arex/?wsdl} \\
\hline
Semantics & \texttt{http://www.nordugrid.org/documents/arex.pdf} \\
\hline
SupportedProfile & \texttt{WS-I 1.0} and \texttt{HPC-BP} \\
\hline
Implementor & \texttt{NorduGrid} \\
\hline
ImplementationName & \texttt{ARC1} \\
\hline
ImplementationVersion & \texttt{0.9} \\
\hline
QualityLevel & \texttt{development} \\
\hline
HealthState & \texttt{ok} -- no detection of problems yet\\
\hline
ServingState & \texttt{draining} if the configuration has allownew=no, \texttt{production} otherwise \\
\hline
IssuerCA & from the \emph{hostcert.pem} file \\
\hline
TrustedCA & from scanning the \emph{certificates} directory \\
\hline
Staging & \texttt{staginginout} \\
\hline
JobDescription & \texttt{ogf:jsdl:1.0}\\
\hline
\end{tabular}

@@

\begin{tabular}{|l|p{12cm}|}
\hline
Property & Value\\
\hline \hline
BaseType & \texttt{Share} \\
\hline
Name & from the configuration \\
\hline
Description & ``comment'' configuration option \\
\hline
MappingQueue & from the configuration \\
\hline
\end{tabular}

\vspace*{3mm}
The following properties are taken from the corresponding values returned by
the LRMS plugin. Units are converted as necessary.

\begin{tabular}{|l|p{12cm}|}
\hline
Property & LRMS plugin property \\
\hline \hline
MaxCPUTime & maxcputime \\
\hline
MinCPUTime & mincputime \\
\hline
DefaultCPUTime & defaultcput \\
\hline
MaxWallTime & maxwalltime \\
\hline
MinWallTime & minwalltime \\
\hline
DefaultWallTime & defaultwallt \\
\hline
\end{tabular}

@@

\begin{tabular}{|l|p{12cm}|}
\hline
Property & Value\\
\hline \hline
MaxTotalJobs & maxjobs from configuration\\
MaxRunningJobs & \\
MaxWaitingJobs & \\
\hline
\end{tabular}

\phantomsection
%\addcontentsline{toc}{subsubsection}{Name}
\hspace*{0.5cm}
\begin{shaded}
\textbf{Name}
\end{shaded}
\begin{tabular}{lp{10cm}}  
Attribute value:& String\\
Example:& \verb#Name: TODO#\\
Related xRSL:& TODO\\
UI role:& ?\\
Description:& Name of the application environment\\
\end{tabular}

\phantomsection
%\addcontentsline{toc}{subsubsection}{Version}
\hspace*{0.5cm}
\begin{shaded}
\textbf{Version}
\end{shaded}
\begin{tabular}{lp{10cm}}  
Attribute value:& String\\
Example:& \verb#Version: TODO#\\
Related xRSL:& TODO\\
UI role:& TODO\\
Description:& Name of the application environment\\
\end{tabular}

>>>>

\vspace*{3mm}
The following properties referring to job counts are calculated based on information in GridManager's status files:

\begin{tabular}{|l|p{12cm}|}
\hline
Property & Meaning \\
\hline \hline
TotalJobs & number of grid jobs in states other than FINISHED \\
\hline
RunningJobs & number of grid jobs in INLRMS:R state \\
\hline
WaitingJobs & number of grid jobs in INLRMS:Q, ACCEPTED, PREPARING and SUBMIT* states \\
\hline
\end{tabular}

@@

\begin{tabular}{|l|p{11cm}|}
\hline
Property & Value\\
\hline \hline
URL & \texttt{https://\emph{hostname}:\emph{port}/arex} \\
\hline
Technology & \texttt{webservice} \\
\hline
Interface & \texttt{OGSA-BES} \\
\hline
WSDL & \texttt{https://\emph{hostname}:\emph{port}/arex/?wsdl} \\
\hline
Semantics & \texttt{http://www.nordugrid.org/documents/arex.pdf} \\
\hline
SupportedProfile & \texttt{WS-I 1.0} and \texttt{HPC-BP} \\
\hline
Implementor & \texttt{NorduGrid} \\
\hline
ImplementationName & \texttt{ARC1} \\
\hline
ImplementationVersion & \texttt{0.9} \\
\hline
QualityLevel & \texttt{development} \\
\hline
HealthState & \texttt{ok} -- no detection of problems yet\\
\hline
ServingState & \texttt{draining} if the configuration has allownew=no, \texttt{production} otherwise \\
\hline
IssuerCA & obtained from the \emph{hostcert.pem} file \\
\hline
TrustedCA & obtained by scanning the \emph{certificates} directory \\
\hline
Staging & \texttt{staginginout} \\
\hline
JobDescription & \texttt{ogf:jsdl:1.0}\\
\hline
\end{tabular}

@@

\begin{tabular}{|l|p{12cm}|}
\hline
Property & Comments \\
\hline \hline
BaseType & \texttt{Share} \\
\hline
Name & from the configuration \\
\hline
Description & ``comment'' configuration option \\
\hline
MappingQueue & from the configuration \\
\hline
SchedulingPolicy & if maui is used, set to \texttt{fairshare} \\
\hline
ServingState & has the same value as Computingendpoint.ServingState \\
\hline
\end{tabular}

\vspace*{3mm}
The following properties are taken from the corresponding attributes returned by
the LRMS plugin. Units are converted as necessary.

\begin{tabular}{|l|p{12cm}|}
\hline
Property & LRMS plugin attribute \\
\hline \hline
MaxCPUTime & maxcputime \\
\hline
MinCPUTime & mincputime \\
\hline
DefaultCPUTime & defaultcput \\
\hline
MaxWallTime & maxwalltime \\
\hline
MinWallTime & minwalltime \\
\hline
DefaultWallTime & defaultwallt \\
\hline
\end{tabular}

@@

The following properties are directly taken from configuration options.

\begin{tabular}{|l|l|p{7cm}|}
\hline
Property & Configuration option  & Comments \\
\hline \hline
MaxTotalJobs & maxjobs & maxjobs is a per cluster limit, grid-manager has no equivalent limit per share \\
\hline
MaxPreLRMSWaitingJobs & maxjobs & \\
\hline
MaxStageInStreams & maxload & maxload is a per cluster limit, grid-manager has no equivalent limit per share \\
\hline
MaxStageOutStreams & maxload & \\
\hline
MaxMemory & nodememory & \\
\hline
MaxDiskSpace & maxdiskperjob & \\
\hline
\end{tabular}

\vspace*{3mm}
The following properties are taken from the corresponding LRMS plugin attributes when available:

\begin{tabular}{|l|p{12cm}|}
\hline
Property & LRMS plugin attribute \\
\hline \hline
MaxRunningJobs & maxrunning \\
\hline
MaxWaitingJobs & maxqueuable - maxrunning \\
\hline
MaxUserRunningJobs & maxuserrun \\
\hline
MaxSlotsPerJob & maxslotsperjob \\
\hline
\end{tabular}

\vspace*{3mm}
The following properties referring to job counts are calculated based on information in GridManager's status files:

\begin{tabular}{|l|p{12cm}|}
\hline
Property & Meaning \\
\hline \hline
TotalJobs &  number of grid jobs in this share in states other than FINISHED \\
\hline
RunningJobs & number of grid jobs in this share in INLRMS:R state \\
\hline
SuspendedJobs & number of grid jobs in this share in INLRMS:S state \\
\hline
WaitingJobs & number of grid jobs in this share in INLRMS:Q and INLRMS:O states \\
\hline
LocalRunningJobs & The total number of jobs running in the associated LRMS queue  minus the number of grid-running grid jobs (RunningJobs) \\
\hline
LocalWaitingJobs & The total number of jobs queued in the associated LRMS queue minus the number of grid-queued grid jobs (WaitingJobs) \\
\hline
StagingJobs & number of grid jobs in this share in PREPARING and FINISHING states \\
\hline
PreLRMSWaitingJobs & number of grid jobs in this share in ACCEPTED, PREPARING and SUBMIT* states\\
\hline
\end{tabular}

\vspace*{3mm}
The following properties are derived from the corresponding LRMS plugin attributes:

\begin{tabular}{|l|p{12cm}|}
\hline
Property & Related LRMS properly \\
\hline \hline
UsedSlots & running \\
\hline
RequestedSlots & queued \\
\hline
FreeSlots & totalcpus - running \\
\hline
FreeSlotsWithDuration & freecpus \\
\hline
\end{tabular}

\subsection{ExecutionEnvironment}

\subsection{ApplicationEnvironment}

\subsection{ComputingActivity}

\subsection{MappingPolicy and AccessPolicy}

%\phantomsection
%%\addcontentsline{toc}{subsubsection}{Name}
%\hspace*{0.5cm}
%\begin{shaded}
%\textbf{Name}
%\end{shaded}
%\begin{tabular}{lp{10cm}}  
%Attribute value:& String\\
%Example:& \verb#Name: TODO#\\
%Related xRSL:& TODO\\
%UI role:& ?\\
%Description:& Name of the application environment\\
%\end{tabular}
